Inferring the effective start dates of non-pharmaceutical interventions during COVID-19 outbreaks

### 2020-05-20 ms/ms.tex
revised model comparison par

We find that a model that considers an NPI (\autoref{eq:NPI_model}) is a better fit to the data than a model without an NPI, i.e. with constant $\beta$ and $\alpha$ (\hl{???}.)
We compare the official $\tau^*$ and effective $\hat{\tau}$ start of NPIs and find that in most regions the effective start of NPI  significantly differs from the official date (\autoref{fig:fig1}). Indeed, the credible interval on $\hat{\tau}$ does not include $\tau^*$ (\autoref{fig:fig1}).
Moreover, we compared the posterior predictive plots of a model with a free $\tau$ with those of a model with $\tau$ fixed at $\tau^*$. The model with free $\tau$ clearly produces better and less variable predictions (\autoref{fig:ppc}).

In the following, we describe our findings on late and early effective start of NPI in detail.

@@

\pagebreak
\begin{multicols}{2}[\section*{References}]
\nolinenumbers
\bibliographystyle{agsm}
%\bibliography{/Users/yoavram/Documents/library}
\bibliography{ms}
\end{multicols}

>>>>

We compared the \hl{posterior predictive plots} of a model with a free $\tau$ with those of a model with $\tau$ fixed at $\tau^*$ and without $\tau$. The model with free $\tau$ clearly produces better and less variable predictions~(\autoref{fig:ppc}). \hl{A similar comparison to no $\tau$.}
However, when we compared the models using WAIC~(\autoref{table:WAIC}), the model with a free parameter for the start of the NPI was better than the other models only in half of the regions.

We compare the official $\tau^*$ and effective $\hat{\tau}$ start of NPIs and find that in most regions the effective start of NPI  significantly differs from the official date (\autoref{fig:fig1}). Indeed, the credible interval on $\hat{\tau}$ does not include $\tau^*$ (\autoref{fig:fig1}).
In the following, we describe our findings on late and early effective start of NPI in detail.

@@

\pagebreak
\begin{multicols}{2}[\section*{References}]
\nolinenumbers
\bibliographystyle{agsm}
\bibliography{/Users/yoavram/Documents/library}
%\bibliography{ms}
\end{multicols}
